Individual and Differential Harm in Redistricting

### 2022-04-12 paper/paper.Rmd
Update paper.Rmd

While we've begun with a two group case, Republicans and Democrats, this can be further extended.
Perhaps we are interested in a third party or the interaction between White and Black with Democrats and Republicans.
This framework allows for us to index by these groups and simply break down the interactions as components of the sum of the harms.

>>>>

This framework easily extends to additional parties or races. For example, we can index for the interaction between White and Black with Democrats and Republicans.
This framework allows for us to index by these groups and simply break down the interactions as components of the sum of the harms.
